% Formatting "borrowed" from http://www.toofishes.net/blog/latex-resume-follow-up/
% Originally used currvita but changed due to masses of excess whitespace

\documentclass[10pt,a4paper]{article}
\usepackage[a4paper,margin=0.5in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{mdwlist}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{tgpagella}
\pagestyle{empty}
\setlength{\tabcolsep}{0em}

% indentsection style, used for sections that aren't already in lists
% that need indentation to the level of all text in the document
\newenvironment{indentsection}[1]%
{\begin{list}{}%
    {\setlength{\leftmargin}{#1}}%
    \item[]%
}
{\end{list}}

% opposite of above, bump a section back toward the left margin
\newenvironment{unindentsection}[1]%
{\begin{list}{}%
    {\setlength{\leftmargin}{-0.5#1}}%
    \item[]%
}
{\end{list}}

% format two pieces of text, one left aligned and one right aligned
\newcommand{\headerrow}[2]
{\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
    #1 &
    #2 \\
\end{tabular*}}

% and the actual content starts here
\begin{document}

\begin{center}
{\LARGE \textbf{Alex Smith}}


alex@alexsmith.org\ \ \textbullet
\ \ Singapore\ \ \textbullet
\ \ http://alexsmith.org
\\
+65 8451 6184 \ \ \textbullet
\ \ https://sg.linkedin.com/in/alexjs
\end{center}

\hrule
\vspace{-0.4em}
\subsection*{Objective}
    My speciality is to engage in any situation and quickly build leadership and direction. I thrive in complex environments with a range of challenges, scaling teams into high performance organisations through ownership and technical intensity.
    \\

\hrule
\vspace{-0.4em}
\subsection*{Experience}

\begin{itemize}
    \parskip=0.1em

    \item
        \headerrow
            {\textbf{Microsoft}}
            {\textbf{Singapore}}
        \\
        \headerrow
            {\emph{Customer Success Unit (CSU) Lead, Azure}}
            {\emph{May 2017 -- Present}}
            
            As the CSU Lead for Microsoft's Azure Cloud, I take care of a 100+ person organisation across Asia Pacific. The CSU team are the most technically deep within the Microsoft field, and help on the acceleration of Cloud adoption and business transformation for Enterprise and Public Sector customers.
            
            \begin{itemize*}
                \item Build a high performance and customer-first organisation
                \item Act as the technical 'last line of defence' for the Asia Pacific organisation
                \item Partner with regulators, governments, and industry bodies to support the secure and compliant adoption of Cloud Computing in all aspects of business
            \end{itemize*}

    \item
            \headerrow
                {\textbf{ICE71 / CyLon}}
                {\textbf{Singapore}}
            \\
            \headerrow
                {\emph{Mentor}}
                {\emph{2017 -- Present}}

                The Innovation Cybersecurity Ecosystem at Block71 (ICE71) is APAC's first cybersecurity entrepreneur hub. As part of the CyLon programme (https://cylonlab.com/), I provide mentoring and guidance to security startups.

    \item
        \headerrow
            {\textbf{Accelerating Asia (and previously muru-D)}}
            {\textbf{Singapore}}
        \\
        \headerrow
            {\emph{Mentor}}
            {\emph{August 2016 -- Present}}

            Accelerating Asia is a regional network of startup programs and an early-stage venture capital fund headquartered in Singapore. The team behind AA are formerly of muru-D, which was the startup accelerator backed by Telstra.
            \\

            I provide guidance and mentoring for early stage startups across various fields including security, technology, micro-finance, health tech, logistics and telecommunications.
    \item
        \headerrow
            {\textbf{Amazon Web Services}}
            {\textbf{Singapore}}
            \\
        \headerrow
            {\emph{Head of Media \& Entertainment Solutions Architecture, APAC}}
            {\emph{December 2014 -- May 2017}}
                
            Established and lead the Media and Entertainment Architecture practice for Amazon Web Services. A hybrid role, providing technical thought leadership, evangelism, architecture and guidance internally and externally.  
                
            \begin{itemize*}
                \item Creating and driving both internal and external go to market strategies and service offerings
                \item Regular global public speaking at both AWS 1\textsuperscript{st} and 3\textsuperscript{rd} party events, while maintaining significant customer engagement, from helping to build Amazon Web Services' profile, to driving adoption and technical excellence
                \item Multi-level engagement, from driving CxO strategy to syscalls
            \end{itemize*}

    \item
        \headerrow
            {\textbf{SwiftServe}}
            {\textbf{Singapore \& Cambridge, UK}}
        \\
        \headerrow
            {\emph{Head of Professional Services}}
            {\emph{October 2013 -- December 2014}}
    
            SwiftServe is a content delivery and security technology provider headquartered in Singapore.
            \\
            Joined to build the Professional Services department, focussed on expanding the capabilities of the network to compete in a quickly changing market. As the technical leader of the Singapore HQ, was heavily involved in the product management lifecycle, representing the user and commercial requirements from across the customer base in the development and network roadmap.
            
            \begin{itemize*}
                \item Lead the development of the Web Application Firewall \& Security project (Layer 7 DDOS protection)
                \item Built Professional Services department from scratch, up to multiple heads and a multi-S\$mm revenue
                \item Extensive technical investigation, resolving high profile incidents and improving overall customer experience
                \item Restructured organisation include Presales, Post Sales, and Professional Services
            \end{itemize*}

    \item
    \headerrow
        {\textbf{Piksel (formerly KIT digital, ioko)}}
        {\textbf{Singapore, Malaysia, \& London, UK}}
    \headerrow
        {\emph{Senior Technical Architect}}
        {\emph{03/2008 -- 10/2013}}

    Piksel provides development, ITIL managed services and technical consultancy/professional services to a range of clients, including Channel 4, BBC, AT\&T, and Disney. Piksel purchased ioko in April 2011 to strengthen their professional services and technical development arm.    

    \begin{itemize*}
        \item Worked as the principal technical authority on multiple projects, mentoring teams of engineers for the successful delivery of high profile platforms.
        \item Primary technical interface to clients, produced high and low level designs, with deep involvement in technical implementations; acted as the SME for a range of products (internal and external) and technologies
        \item Key account contact for multiple customers, instrumental in both client retention and account development
        \item Developed in-house skunkworks-style projects which have been adopted into the product development organization, which form part of customer production systems
    \end{itemize*}
    \subsection*{\emph{Notable Projects}}
        \begin{itemize}
            \item 
            \headerrow
                {\textbf{Celcom, Axiata Group Berhad}}
                {\textbf{Kuala Lumpur, Malaysia}}
            \\
            \headerrow
                {\emph{Senior Technical Architect}}
                {\emph{2012 - 2013}}
                Video on Demand project, to deliver premium content to existing cellular subscribers. Lead the project as the Platform Architect, specialised in the development of automated deployment systems and platform content delivery strategy. Integration with OSS \& BSS services.
            \item 
            \headerrow
                {\textbf{Channel 4 Television Corporation}}
                {\textbf{London, UK}}
            \\
            \headerrow
                {\emph{Lead Infrastructure Architect}}
                {\emph{2010 - 2012}}
                Channel 4 is the UK's alternative public broadcaster, and one of the first adopters of Public Cloud. Leading Architect on a range of services, and final line of technical escalation for production issues.
                \begin{itemize*}
                    \item Development and implementation of an Cloud Management System across all Amazon Web Services and Private Cloud hosted sites
                    \item Lead Architect on projects including:
                    \begin{itemize*}
                        \item 4oD on PS3, iOS, and XBox 360 (IBC 2012 Innovation in Content Delivery Award)
                        \item Full Platform Re-architecture (incl. migration to Amazon Web Services)
                    \end{itemize*}
                \end{itemize*}
        
            \item 
            \headerrow
                {\textbf{FilmFlex (Film4oD, Virgin On Demand, hmv on-demand)}}
                {\textbf{London, UK}}
            \\
            \headerrow
                {\emph{Infrastructure Platform Owner / Architect}}
                {\emph{2009 - 2013}}
                FilmFlex was a UK Movies on Demand service. FilmFlex was purchased in 2014 by Vubiquity.
            \item 
            \headerrow
                {\textbf{SeeSaw.com / Project Kangaroo}}
                {\textbf{London, UK}}
            \\
                Project Kangaroo was initially an OTT venture by the BBC, Channel 4 and ITV, later launched as SeeSaw.com by Arqiva. Became lead project engineer, and lead the architecture of the data warehousing and BI suite.
            \item 
            \headerrow
                {\textbf{FOXTEL}}
                {\textbf{Sydney, Australia}}
            \\
                FOXTEL is an Australian television company. Relocated to Australia to provide technical assurance for meeting aggressive launch for the new FOXTEL on Xbox platform.
            \item 
            \headerrow
                {\textbf{BBC Monitoring}}
                {\textbf{UK}}
            \\
                BBC Monitoring is a commercial arm of the BBC, providing signal intelligence across various data sources.
        \end{itemize}

    \item
        \headerrow
            {\textbf{Venda, Inc.}}
            {\textbf{London, UK}}
        \\
        \headerrow
            {\emph{Systems Administrator}}
            {\emph{2007 -- 2008}}
    
            Venda, Inc. was the world's largest SaaS e-commerce provider. Their PCI-DSS Tier-1 compliant platform handled hundreds of financial transactions per second. Venda was acquired in 2014 by NetSuite Inc, and Oracle in 2016.
    \item
        \headerrow
            {\textbf{aql}}
            {\textbf{Leeds, UK}}
        \\
        \headerrow
            {\emph{Systems Support \& Software Development (PT)}}
            {\emph{2004 -- 2006 (various)}}
    
            aql are an award winning VoIP, datacentre and hosting company based in the UK.
\end{itemize}


\hrule
\vspace{-0.4em}
\subsection*{Core Skills}

\begin{indentsection}{\parindent}
\hyphenpenalty=1000
\begin{description*}
    \item[Business:]
    Public Speaking, Product Management, Solution Development , Organisational Growth, 
    \item[Technologies:]
    Microsoft Azure, Amazon Web Services, HTTP Technologies [Caching, Nginx/Varnish/Apache/STM], Automation [Puppet, Chef], Performance Optimisation [JVM, PHP, Python, Ruby], Databases [MongoDB, Oracle RDBMS, MySQL, PgSQL] Virtualisation [VMware, Xen, KVM], Media [Encoding, Packaging, Protocols]
    \item[Languages:]
    Write: [Python, \LaTeX, Perl, shell script, SQL, Japanese (JLPT N4)]; Read: [Java, C, C++, Ruby, PHP, etc.]
\end{description*}
\end{indentsection}

\hrule
\vspace{-0.4em}
\subsection*{Notable Public Speaking Engagements}
    \headerrow
        {Achieving Security, Agility and Flexibility in the Cloud (Broadcast Asia, 2016)}
        {June 2016}
    \headerrow
        {Digital Culture; Logging at Scale; JS Development Deep Dives (AWS Summits - MY, SG, PH, TW, KR)}
        {Apr 2016}
    \headerrow
        {Pure Play Video OTT: A Microservices Architecture in the Cloud (AWS re:Invent 2015 - Las Vegas, US)}
        {Oct 2015}
    \headerrow
        {CDN Federation in South East Asia (AIMS Customer Conference - Kuala Lumpur, MY)}
        {Nov 2014}
    \headerrow
        {Web Security Innovation (Conversant Annual Conference - Shanghai, CN)}
        {Oct 2014}
\\
\hrule
\vspace{-0.4em}
\subsection*{Awards}
    \headerrow
        {Worldwide Commercial Sales Award - APAC (Amazon Web Services)}
        {2016}
    \headerrow
        {Best Technical Innovation (Scrapbook, Channel4) - Online Media Awards}
        {Aug 2013}
    \headerrow
        {Innovation Award for Content Delivery (4oD on Xbox, Channel 4) - IBC}
        {Sept 2012}
% \subsection*{Volunteering}
%     \headerrow
%         {Provided technology consulting services for mySociety, no2id, and the Open Rights Group.}

\end{document}
